Increasing quality of self-recovering images using BPCS Steganography

### 2014-11-04 Paper/main.tex
Section 5 proof read

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"lena"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImage"}%
}%
\caption{Embedding Once. Left: Original Image, Right: Image After embedding}
\label{fig:lenaEmbedOnceEmbedding}
\end{figure}

@@

\hspace{0pt} \\
The next step in the experiment conducted was to modify the image after embedding.
\begin{figure}[h]
	\centerline{%
	\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImage - Copy"}%
	}%
	\caption{Image After Tampering}
	\label{fig:lenaEmbedOnceTampered}
\end{figure}
After the image was modified it was reconstructed using the method described in \ref{extractRestore}.
The results of this reconstruction can be seen in figure \ref{fig:lenaEmbedOnceRestoredOriginal}, showing the original image and the image after reconstruction.

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"lena"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImageAfterRestoration"}%
}%
\caption{Left: Original Image, Right: Image After Reconstruction}
\label{fig:lenaEmbedOnceRestoredOriginal}
\end{figure}

@@

\hspace{0pt} \\
The experimentation process thus shows that if the image reference content is only embedded once into the original image that the quality of the image after embedding as well as the quality of the image after reconstruction is relatively high.
It was however found that the tamper rate possible was quite low at \textless 3\%.
To attempt to remedy this problem another instance of the experiment was run with the only independent variable being the fact that the image reference content was now being embedded twice.
This increases the probability reconstruction will be possible since every piece of image reference content is contained twice in the image after embedding.
A specific piece of the image reference content must thus be lost in two locations before reconstruction is no longer possible.
The results can be seen in figure \ref{fig:lenaEmbedTwiceEmbedding}, figure \ref{fig:lenaEmbedTwiceTampered} and figure \ref{fig:lenaEmbedTwiceRestoration}

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"lena"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Lena Embed twice 0.7 threshold/finalImage"}%
}%
\caption{Embedding Twice. Left: Original Image, Right: Image After embedding}
\label{fig:lenaEmbedTwiceEmbedding}
\end{figure}

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"Lena Embed twice 0.7 threshold/finalImage - Copy"}%
}%
\caption{Embedding Twice. Image After Tampering}
\label{fig:lenaEmbedTwiceTampered}
\end{figure}

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"lena"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Lena Embed twice 0.7 threshold/finalImageAfterRestoration"}%
}%
\caption{Embedding Twice. Left: Original image, Right: Image After Restoration}
\label{fig:lenaEmbedTwiceRestoration}
\end{figure}

@@

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.3375]{"tree"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Tree Embed once 0.8 threshold/finalImage"}%
}%
\caption{Embedding Once. Left: Original Image, Right: Image After embedding}
\label{fig:treeEmbedOnceEmbedding}
\end{figure}

@@

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"Tree Embed once 0.8 threshold/finalImage - Copy"}%
}%
\caption{Embedding Once. Image After Tampering}
\label{fig:treeEmbedOnceTamper}
\end{figure}

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.3375]{"tree"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Tree Embed once 0.8 threshold/finalImageAfterRestoration"}%
}%
\caption{Embedding Once. Left: Original image, Right: Image After Restoration}
\label{fig:treeEmbedOnceRestore}
\end{figure}

@@

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.3375]{"tree"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Tree Embed twice 0.8 threshold/finalImage"}%
}%
\caption{Embedding Twice. Left: Original Image, Right: Image After embedding}
\label{fig:treeEmbedTwiceEmbedding}
\end{figure}

@@

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"Tree Embed twice 0.8 threshold/finalImage - Copy"}%
}%
\caption{Embedding Twice. Image After Tampering}
\label{fig:treeEmbedTwiceTamper}
\end{figure}

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.3375]{"tree"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Tree Embed twice 0.8 threshold/finalImageAfterRestoration"}%
}%
\caption{Embedding Twice. Left: Original image, Right: Image After Restoration}
\label{fig:treeEmbedTwiceRestore}
\end{figure}

\hspace{0pt} \\
The PSNR of the image after reconstruction was 26.05dB.
The tamper rate, as was the case with the first image image (figure \ref{fig:lenaEmbedTwiceRestoration}), was increased from \textless 3\% to \textless 35\% with a similar reduction in quality experienced.
\begin{center}
  \begin{tabular}{| l | l | l | l |}
    \hline
    \multicolumn{4}{|c|}{Experimental results summary} \\
    \hline
    Image & PSNR after embedding & PSNR after restoration & Tampering rate \\ \hline
    Figure \ref{fig:lenaEmbedOnceEmbedding} - \ref{fig:lenaEmbedOnceRestoredOriginal} (Embed once) & 34.92dB & 34.89dB & \textless 3\% \\ \hline
    Figure \ref{fig:lenaEmbedTwiceEmbedding} - \ref{fig:lenaEmbedTwiceRestoration} (Embed twice) & 34.92dB & 32.52 dB & \textless 35\% \\ \hline
    Figure \ref{fig:treeEmbedOnceEmbedding} - \ref{fig:treeEmbedOnceRestore} (Embed once) & 27.94dB & 27.72dB & \textless 3\% \\ \hline
    Figure \ref{fig:treeEmbedTwiceEmbedding} - \ref{fig:treeEmbedTwiceRestore} (Embed twice) & 27.93dB & 26.05dB & \textless 35\% \\ \hline
    \hline
  \end{tabular}
\end{center}

\hspace{0pt} \\
The second image used thus behaved in a similar manner to the first image with the only significant difference being the much lower PSNR values produced.
This is due to the fact that the embedding algorithm used dynamically determines where to embed the image reference content depending on the original image.
Areas in the second image like the grass and tree leaves are detected by the embedding algorithm as noisy and suitable for embedding, the second image thus has more space to embed information in without introducing noticeable visual distortion than the first image.
The PSNR method used to objectively measure the quality of the images gives a lower quality rating due to more of the image being different from the original image even though when observed visually the image does not appear to have undergone such a big change. 
  As an experimental control the results from the experiment in the proposed method is compared to other current methods for images with self-recovering capabilities.
This is discussed further in  section \ref{interpretation}.

@@

\hspace{0pt} \\
Research in \cite{wang2002image} points out several shortcomings of methods of measuring and comparing image quality using methods such as PSNR. 
PSNR is a useful measure for objective image quality assessment to a certain degree, however there are other important factors to consider. 
The one important factor is how a person would perceive the image quality.
Another important factor is if the meaning of the image is still clear even after reconstruction.
This would typically mean being able to identify key features of the image easily. 
The proposed method performs well under this form a visual analysis.

@@

\hspace{0pt} \\
The embedding rate and effects of the embedding rate seemed consistent across the different images used.
The embedding rate was low where the image reference content was only embedded once into the original image and compared poorly to methods such as the dynamic block allocation method.
However it was found that if the image reference content is embedded twice into the original image that the tamper rate compares equally to that of dynamic block allocation method.

>>>>

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"lena"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImage"}%
}%
\caption{Left: Original image, Right: Image after embedding}
\label{fig:lenaEmbedOnceEmbedding}
\end{figure}

@@

\hspace{0pt} \\
The next step in the experiment conducted was to modify the image after embedding (figure \ref{fig:lenaEmbedOnceTampered}).
\begin{figure}[h]
	\centerline{%
	\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImage - Copy"}%
	}%
	\caption{Image after tampering}
	\label{fig:lenaEmbedOnceTampered}
\end{figure}
After the image was modified it was reconstructed using the method described in section \ref{extractRestore}.
The results of this reconstruction can be seen in figure \ref{fig:lenaEmbedOnceRestoredOriginal}, showing the original image and the image after reconstruction.

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"lena"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Lena Embed once 0.7 threshold/finalImageAfterRestoration"}%
}%
\caption{Left: Original image, Right: Image after reconstruction}
\label{fig:lenaEmbedOnceRestoredOriginal}
\end{figure}

@@

\hspace{0pt} \\
The experimentation process thus shows that if the image reference content is only embedded once into the original image that the quality of the image after embedding as well as the quality of the image after reconstruction is relatively high.
It was however found that the tamper rate possible was quite low at \textless 3\%.
To attempt to remedy this problem another instance of the experiment was run with the only independent variable being the fact that the image reference content was now being embedded twice.
This increases the probability that reconstruction will be possible since every piece of image reference content is contained twice in the image after embedding.
A specific piece of the image reference content must thus be lost in two locations before reconstruction is no longer possible.
The results can be seen in figure \ref{fig:lenaEmbedTwiceEmbedding}, figure \ref{fig:lenaEmbedTwiceTampered} and figure \ref{fig:lenaEmbedTwiceRestoration}

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"lena"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Lena Embed twice 0.7 threshold/finalImage"}%
}%
\caption{Embedding twice. Left: Original image, Right: Image after embedding}
\label{fig:lenaEmbedTwiceEmbedding}
\end{figure}

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"Lena Embed twice 0.7 threshold/finalImage - Copy"}%
}%
\caption{Embedding twice. Image after tampering}
\label{fig:lenaEmbedTwiceTampered}
\end{figure}

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"lena"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Lena Embed twice 0.7 threshold/finalImageAfterRestoration"}%
}%
\caption{Embedding twice. Left: Original image, Right: Image after reconstruction}
\label{fig:lenaEmbedTwiceRestoration}
\end{figure}

@@

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.3375]{"tree"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Tree Embed once 0.8 threshold/finalImage"}%
}%
\caption{Embedding once. Left: Original image, Right: Image after embedding}
\label{fig:treeEmbedOnceEmbedding}
\end{figure}

@@

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"Tree Embed once 0.8 threshold/finalImage - Copy"}%
}%
\caption{Embedding once. Image after tampering}
\label{fig:treeEmbedOnceTamper}
\end{figure}

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.3375]{"tree"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Tree Embed once 0.8 threshold/finalImageAfterRestoration"}%
}%
\caption{Embedding once. Left: Original image, Right: Image after reconstruction}
\label{fig:treeEmbedOnceRestore}
\end{figure}

@@

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.3375]{"tree"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Tree Embed twice 0.8 threshold/finalImage"}%
}%
\caption{Embedding twice. Left: Original image, Right: Image after embedding}
\label{fig:treeEmbedTwiceEmbedding}
\end{figure}

@@

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.45]{"Tree Embed twice 0.8 threshold/finalImage - Copy"}%
}%
\caption{Embedding twice. Image after tampering}
\label{fig:treeEmbedTwiceTamper}
\end{figure}

\begin{figure}[h]
\centerline{%
\includegraphics[scale=0.3375]{"tree"}%
\hspace{0.1cm}
\includegraphics[scale=0.45]{"Tree Embed twice 0.8 threshold/finalImageAfterRestoration"}%
}%
\caption{Embedding twice. Left: Original image, Right: Image after reconstruction}
\label{fig:treeEmbedTwiceRestore}
\end{figure}

\hspace{0pt} \\
The PSNR of the image after reconstruction was 26.05dB.
The tamper rate, as was the case with the first image image (figure \ref{fig:lenaEmbedTwiceRestoration}), was increased from \textless 3\% to \textless 35\% with a similar reduction in quality experienced.
\begin{center}
  \begin{tabular}{| l | l | l | l |}
    \hline
    \multicolumn{4}{|c|}{Experimental results summary} \\
    \hline
    Image & PSNR after embedding & PSNR after restoration & Tamper rate \\ \hline
    Figure \ref{fig:lenaEmbedOnceEmbedding} - \ref{fig:lenaEmbedOnceRestoredOriginal} (Embed once) & 34.92dB & 34.89dB & \textless 3\% \\ \hline
    Figure \ref{fig:lenaEmbedTwiceEmbedding} - \ref{fig:lenaEmbedTwiceRestoration} (Embed twice) & 34.92dB & 32.52 dB & \textless 35\% \\ \hline
    Figure \ref{fig:treeEmbedOnceEmbedding} - \ref{fig:treeEmbedOnceRestore} (Embed once) & 27.94dB & 27.72dB & \textless 3\% \\ \hline
    Figure \ref{fig:treeEmbedTwiceEmbedding} - \ref{fig:treeEmbedTwiceRestore} (Embed twice) & 27.93dB & 26.05dB & \textless 35\% \\ \hline
    \hline
  \end{tabular}
\end{center}

\hspace{0pt} \\
The second image used thus behaved in a similar manner to the first image with the only significant difference being the much lower PSNR values produced.
This is due to the fact that the embedding algorithm used dynamically determines where to embed the image reference content depending on the original image.
Areas in the second image like the grass and tree leaves are detected by the embedding algorithm as noisy and suitable for embedding. 
The second image thus has more space than the first image to embed information in without introducing noticeable visual distortion.
The PSNR method used to objectively measure the quality of the images gives a lower quality rating due to more of the image being different from the original image even though when observed visually the image does not appear to have undergone such a big change. 
  As an experimental control the results from the experiment in the proposed method is compared to other current methods for images with self-recovering capabilities.
This is discussed further in  section \ref{interpretation}.

@@

\hspace{0pt} \\
Research in \cite{wang2002image} points out several shortcomings of measuring and comparing image quality using methods such as PSNR. 
PSNR is a useful measure for objective image quality assessment to a certain degree, however there are other important factors to consider. 
The one important factor is how a person would perceive the image quality.
Another important factor is if the meaning of the image is still clear even after reconstruction.
This would typically mean being able to identify key features of the image easily. 
The proposed method performs well under this form a visual analysis.

@@

\hspace{0pt} \\
The tamper rate seemed consistent across the different images used.
The tamper rate was low where the image reference content was only embedded once into the original image and compared poorly to methods such as the dynamic block allocation method.
However it was found that if the image reference content is embedded twice into the original image that the tamper rate compares equally to that of dynamic block allocation method.
